Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-13 GWLDCII.tex
assimilating some of Susama's edits into paper 2

These diagrams correspond to (tree level) amplitudes of SYM N=4 theory in twistor space. As such, it associates a real value to $n$ particles, one for each vertex. Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}. In otherwords, each Wilson loop diagram defines a functional on external particles. This is represented as an integral $I(W)$, which is the equalent of a Feynman integral in this setting.

A $n \times |\cP|$ matrix $C(W)$ represents the (tree level) particle interactions. Each row of $C(W)$ corresponds to an internal propagator, each column to an external particle. Each row only has zero entries on every external particle it does not interact with. In particular,

@@

The entries $c_{p,q}$ are non-zero real variables. This matrix can be interpreted as a parametrization of the positroid cell in the positive Grassmannian $\Gr(n, |\cP|)$ assoiciated to the $W$, call it $\Sigma(W)$ \cite{wilsonloops}. Most of the work in this paper, and in \cite{GWLDI} focuses on characterizing the positroid cell assoicated to eash Wilson loop diagram $W$. An example of $C(W)$ is given in example \ref{integraldetails}.

Note that, since there is no ordering on the propagators of $W$, $C(W)$ is only defined up to rearrangement of the rows. This will not matter as this does not effect the parametrization of $\Sigma(W)$.

One may also interpret functional $I(W)$ as a associating a volume to each $\Sigma(W)$ \cite{wilsonloops, AmplituhedronSquared, HeslopStewart}. The volume form is written in terms of the elements of $C(W)$as  \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \]
The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.

For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is finite \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}: \bas \mathcal{A}_{k, n}^{tree} = \sum_{(\cP, [n]), |\cP| = k} I(W) <\infty \eas for all sets of external particles.Therefore, any singularities in the integral $I(W)$ must cancel in the sum. In particular, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}. This has been checked for particular classes of examples, \cite{casestudy, AmplituhedronSquared, HeslopStewart}, but has not been proven in general.

In this paper, we consider the denominator $R(W)$, which we define next.

@@

In section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ the structure of $W$, as encapulated by $C(W)$. In fact, it can be read directly off of $C(W)$, given a characterizeation of $\Sigma(W)$ called the Grassmann necklace. We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.

We end this section with an example illustration $C(W)$ $R(W)$.

@@

To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \eas
\end{eg}

@@

\begin{rmk}
While this paper primarily approaches proofs from a combinatorial point of view, readers with a background in matroid theory are encouraged to keep the matroidal viewpoint in mind throughout; we expect that the two approaches will be complementary and will build upon each other. See [ref][paper 1] for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
\end{rmk}

@@

\note{Sian thinks that a section roadmap here would be overkill: we gave a roadmap in section 1, each subsection has its own little intro roadmap, and I've added a ref to the algorithm above so that people can skip straight to it if they want}
%In Section~\ref{sec:propagator configs} we examine the structure of admissible Wilson loop diagrams and prove several technical lemmas about configurations of propagators appearing in these diagrams. In Section~\ref{sec:GN alg} we state the algorithm that extracts the Grassmann necklace of a given diagram (see Algorithm~\ref{alg:put GN on WLD}) and

@@

% Observe that changing the direction of the propagator simply swaps the inside and outside sets, i.e. for $p = (i,j)$ we have 
% \[\cP_{in}(p, <_i) = \cP_{out}(p, <_j)\quad \text{ and } \quad \cP_{out}(p, <_i) = \cP_{in}(p, <_j).\]

\begin{eg}
Let $W$ be the Wilson loop diagram from Figure \ref{fig:ex of WLD}, reproduced here for convenience.  \[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $p$}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture}\]

@@

%Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can construct two obvious subdiagrams of $W$ by just removing all of the propagators on one side of $p$ and leaving the vertices intact, i.e. the subdiagrams
%\[  (\cP_{in}(p,<_i), [n])  \quad \textrm{and} \quad  (]cP_{out}(p,<_i), [n]).\]

@@

\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{20}{1.5}
	%\drawnumbers
	%\drawprop{1}{0}{4}{0}
	\drawlabeledprop{5}{0}{7}{0}{\footnotesize $p_1$}
    \drawlabeledprop{3}{0}{12}{0}{\footnotesize $q_1$}
		\end{scope}
	\end{tikzpicture}\eas

\hlfix{INSERT PICTURE HERE?}{note highlighting this for anyone skimming through looking for pictures to add}

@@

Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses. Therefore without loss of generality we may assume that {\color{violet}$\cP_{in}(q_r)$ does not contain a propagator (other than $q_r$ itself)} \st{$q_r$ is the innermost propagator of length $\geq 4$ in $W_r$} which satisfies the induction hypotheses, i.e. we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.

@@

Specifically, for each $i$ in the support of $p$, define the set
\[J_p^{W}(i) = \{m \in [n] \ | \ I^{W}_m(p) = i \},\]
the set of starting vertices $m$ such that $I_m^{W}$ assigns $p$ to $i$.

@@

\begin{proof}
We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ {\color{violet} (possibly weakly admissible)} with $F(\emptyset) = \emptyset$.  Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation), although this region may or may not contain non-supporting vertices which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).

@@

Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.  In this case, the vertices $\{l,l+1,l+2,l+3 \}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{V} = J_r^{W}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.  Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{W}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{W}(l) = [n] \backslash \{l+1, l+2, l+3\}$. The result therefore holds in this case.

@@

In $V$ there are no propagators inside $q$, so we see from Figure \ref{fig V diagram} that
\[l, l+1, \ldots ,j \in J^{V}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{V}_q(j+1).\]
Note that $j+2 \not\in J^{V}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so  $J^{V}_q(j+1) = \{j+1\}$ and \hlfix{by the induction hypothesis we must have}{moved} $j+2 \in J^{V}_q(i)$. Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
\ba J^{V}_q(i) = [j+2,d-1], \quad J^{V}_q(i+1) = [d,e-1], \quad J^{V}_q(j) = [e,j], \quad J^{V}_q(j+1) = \{j+1\}, \label{deeqs}\ea
and all intervals are non-empty.

@@

\textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously. \hlfix{Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.}{moved} Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$ (note that there is at least 1); so these vertices are $l, \ldots, l+a-1$.  Note that these non-supporting vertices are all in the support of $p$.

We first calculate \hlfix{$I^{W}_w(?)$}{which prop(s), as a function?} for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, {\color{violet}(if $r \neq p$, $I_w^W(r) = I_w^V(r)$)} while the value of $I^{W}_w(p)$ depends on \st{how soon $q$ is assigned to a vertex, i.e. on}\sanote{don't like the phrasing ``soon''} the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the \hlfix{majority}{$w \in [l, l+a-1]$} of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by \hlfix{$I_w^{W}$, then the remainder of $I_w^{W}$}{$I_w$ instead of $I_w^W$?} proceeds identically to the assignments of $I^{V}_{w+1}$.  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

Consider the \st{WLD} {\color{violet} weakly admissible Wilson loop diagram}\sanote{actually, I think this is admissible, because we are removing a propagator from a weakly admissible. But it needs a few words?} $X$ formed from $V$ by \st{moving the second end of $q$ to the edge $j-1$ instead of $j$} {\color{violet} replacing the propagator $q = (i,j)$ with $q = (i, j-1)$}.  $X$ is still {\color{violet}weakly} admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well. Note that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ {\color{violet}and in particular for $r=q$. Further, } \st{and} $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  Additionally $I_{j+1}^{X}(q) = i$ \st{by the induction hypothesis applied to $X$}, {\color{violet}because} \st{and so} if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.  Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$. Therefore
       \[
       I_j^{W}(r) = \begin{cases}

       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
       I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
       \] 
Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
\[
       I_{j+1}^{W}(r)  = \begin{cases}
         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
         I_{j+2}^{V}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
       \end{cases}
       \]
Now suppose $j+1$ is not in the support of $p$. If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$. We already know that $J_q^{V}(j+1) = \{j+1\}$; \hlfix{in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$}{why? It is true but what does it follow from? The next few lines?}.  However the construction of $I^{V}_{j+1}$ first associates $q$ to $j+1$ and \hlfix{then proceeds identically to $I^{V}_{j+2}$.}{We use this fact a lot should it be a lemma?}  In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.

>>>>

These diagrams correspond to (tree level) amplitudes of SYM $N=4$ theory in twistor space. As such, it associates a real value to $n$ particles, one for each vertex. Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}. In other words, each Wilson loop diagram defines a functional on external particles. This is represented as an integral $I(W)$, which is the equivalent of a Feynman integral in this setting.

A $|\cP| \times n$ matrix $C(W)$ represents the (tree level) particle interactions. Each row of $C(W)$ corresponds to an internal propagator, each column to an external particle. $C(W)$ is defined as follows:

@@

The entries $c_{p,q}$ are non-zero real variables. Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with. See \ref{integraldetails} for an example of a diagram $W$ and its associated matrix.

The matrix $C(W)$ can be interpreted as a parametrization of the positroid cell in the positive Grassmannian $\Gr(n, |\cP|)$ associated to the $W$, which we denote by $\Sigma(W)$ \cite{wilsonloop}. Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell assoicated to eash Wilson loop diagram $W$.

Note that since there is no ordering on the propagators of $W$, $C(W)$ is only defined up to rearrangement of the rows. This will not matter here, as it does not affect the parametrization of $\Sigma(W)$.

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}. The volume form is written in terms of the elements of $C(W)$ as  \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \]
The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.

For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size. By \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha} this sum is finite for all sets of external particles, i.e. we have \bas \mathcal{A}_{k, n}^{tree} = \sum_{(\cP, [n]), |\cP| = k} I(W) <\infty. \eas

In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum. In particular, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}. This has been checked for particular classes of examples (e.g. \cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.

With this motivation in mind, in this paper we study the denominator $R(W)$ of the volume form $\Omega(W)$, which we define next.

@@

In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$. In fact, it can be read directly off of $C(W)$, in terms of characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}). We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.

We end this section with an example of computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.

@@

To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \eas
\note{Is the numerator just supposed to be the product of $dc_{pq}$ for each $c_{pq}$ in the matrix? Also I think $c_{46}c_{35} - c_{36}c_{45}$ in the denominator is the wrong way around?}
\end{eg}

@@

\begin{rmk}
While this paper primarily approaches proofs from a combinatorial point of view, readers with a background in matroid theory are encouraged to keep the matroidal viewpoint in mind throughout; we expect that the two approaches will be complementary and will build upon each other. See \cite{generalcombinatoricsI} for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
\end{rmk}

@@

%\note{Sian thinks that a section roadmap here would be overkill: we gave a roadmap in section 1, each subsection has its own little intro roadmap, and I've added a ref to the algorithm above so that people can skip straight to it if they want}

%In Section~\ref{sec:propagator configs} we examine the structure of admissible Wilson loop diagrams and prove several technical lemmas about configurations of propagators appearing in these diagrams. In Section~\ref{sec:GN alg} we state the algorithm that extracts the Grassmann necklace of a given diagram (see Algorithm~\ref{alg:put GN on WLD}) and

@@

\begin{eg}
Let $W$ be the Wilson loop diagram from Figure \ref{fig:ex of WLD}, reproduced here for convenience.  \[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{0}{4}{0}{\footnotesize \qquad \ $p$}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture}\]

@@

@@

\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{15}{2}
	%\drawnumbers
	%\drawprop{1}{0}{4}{0}
	\begin{scope}
	\clip (0,0) circle (\radius cm);
	\draw[propagator] (\angle*5.3:\radius*1.2cm) to [bend left=50] (\angle*7.7:\radius*1.2cm);
	\node at (\angle*6.5:\radius*0.6cm) {\footnotesize $p_1$};
	\end{scope}
    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$}
    	\node at (\angle*5:\radius*1.15cm) {\footnotesize $j_1$};
    	\node at (\angle*10:\radius*1.15cm) {\footnotesize $i_1$};
		\end{scope}
	\end{tikzpicture}\eas

\note{Sian note to self: come back and check this later, if we end up with code for drawing partial diagrams then that might make a better diagram}

@@

Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses. Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e. we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.

@@

Specifically, for each $i$ in the support of $p$ we define the set
\[J_p^{W}(i) = \{m \in [n] \ | \ I^{W}_m(p) = i \},\]
the set of starting vertices $m$ such that $I_m^{W}$ assigns $p$ to $i$.

@@

\begin{proof}
We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with $F(\emptyset) = \emptyset$.  Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.

@@

Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.  In this case, the vertices ${\{l,l+1,l+2,l+3\}}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{V} = J_r^{W}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.  Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{W}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{W}(l) = [n] \backslash \{l+1, l+2, l+3\}$. The result therefore holds in this case.

@@

In $V$ there are no propagators inside $q$ by construction, so we see from Figure \ref{fig V diagram} that
\[l, l+1, \ldots ,j \in J^{V}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{V}_q(j+1).\]
Note that $j+2 \not\in J^{V}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so  $J^{V}_q(j+1) = \{j+1\}$ and by the induction hypothesis we must have $j+2 \in J^{V}_q(i)$. Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
\ba J^{V}_q(i) = [j+2,d-1], \quad J^{V}_q(i+1) = [d,e-1], \quad J^{V}_q(j) = [e,j], \quad J^{V}_q(j+1) = \{j+1\}, \label{deeqs}\ea
and all intervals are non-empty.

@@

\textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously. Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$. Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$ (note that there is at least 1); so these vertices are $l, \ldots, l+a-1$.  Note that these non-supporting vertices are all in the support of $p$.

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$.  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$; \note{Added a note about $V$ being admissible when we defined it, so we can use $X$ admissible here without comment} $X$ is still admissible since we have not decreased the support of any set of propagators. 
% From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
It follows from the position of $q$ in $X$ that $I_j^X(q) = j$, and from Lemma~\ref{lem no fourth vertex} that $I_{j+1}^X(q) \neq j$. By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$; in particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.

Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$. We obtain
       \[
       I_j^{W}(r) = \begin{cases}

       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
       I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
       \] 
This completes the analysis of $I_j^W$. Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
\[
       I_{j+1}^{W}(r)  = \begin{cases}
         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
         I_{j+2}^{V}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
       \end{cases}
       \]
Now suppose $j+1$ is not in the support of $p$. If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$. We already know that $J_q^{V}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$, by the induction hypothesis applied to $V$. However the construction of $I^{V}_{j+1}$ first assigns $q$ to $j+1$ and then proceeds identically to $I^{V}_{j+2}$.  In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.

Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in the algorithm for $I_{j+1}^W$, and
    \[
    I_{j+1}^{W}(r)  = \begin{cases}
      m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
      I_{j+1}^{V}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
    \end{cases}
    \]
We can now describe the intervals $J^{W}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}. For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{W}(*)$ as follows. Recall that $p = (m,m+2)$, $1 \leq a \leq 3$ is the number of non-supporting vertices inside $q$ in $V$, and these non-supporting vertices are denoted $\{l,l+1, \dots\}$. 
    \begin{itemize}
      \item 
    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
    \begin{gather*}
    J^{W}_p(m) = [m+4, m], \qquad  J^{W}_p(m+1) = \{m+1\}, \\ J^{W}_p(m+2) = \{m+2\}, \qquad  J^{W}_p(m+3) = \{m+3\},
    \end{gather*}
    which are nonempty and otherwise as required.
  \item
        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
    \begin{gather*}
    J^{W}_p(m) = [m+4, d-1], \qquad  J^{W}_p(m+1) = [d, m+1], \\  J^{W}_p(m+2) = \{m+2\}, \qquad  J^{W}_p(m+3) = \{m+3\},
    \end{gather*}
    which are nonempty and otherwise as required. Recall that $d$ was defined in equation \eqref{deeqs}.
  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
    \begin{gather*}
    J^{W}_p(m) = \{m+4\}, \qquad  J^{W}_p(m+1) = [m+5, d-1], \\  J^{W}_p(m+2) = [d, m+2], \qquad  J^{W}_p(m+3) = \{m+3\},
    \end{gather*}
    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
    \begin{gather*}
    J^{W}_p(m) = [m+4, j+1], \qquad  J^{W}_p(m+1) = [j+2, d-1], \\  J^{W}_p(m+2) = [d, m+2], \qquad  J^{W}_p(m+3) = \{m+3\},
    \end{gather*}
    which are again as required.
    \end{itemize}
